Supporting Information

### 2018-03-20 SupportingInformation.Rmd

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
#source("TaylorsLawTools.R")

#We are only doing spatial taylor's law because we know a priori temporal
#won't give anything interesting for the surrogates we use

#kend.stats.res<-list()
#kend.points.res<-list()
#spea.stats.res<-list()
#spea.points.res<-list()
#for (counter in 1:length(kend.surrog))
#{
 # ks<-kend.surrog[[counter]]
#  ss<-spea.surrog[[counter]]
 # kend.stats.res[[counter]]<-matrix(NA,5,numdat)
#  spea.stats.res[[counter]]<-matrix(NA,5,numdat)
 # kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
  #spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
  #for (sc in 1:numdat)
  #{
   # khold<-tl_stats(ks[,,sc])
  #  kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
   # rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
    #kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)

    #shold<-tl_stats(ss[,,sc])
    #spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
    #rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
    #spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
  #}
#}
#names(kend.stats.res)<-names(kend.surrog)
#names(kend.points.res)<-names(kend.surrog)
#names(spea.stats.res)<-names(spea.surrog)
#names(spea.points.res)<-names(spea.surrog)

#DAN: now you want to compare whether tl held, and the slope (statistically and visually)
#across the different elements of kend.XX.res and spea.XX.res. See drawing of a figure layout on desk.

>>>>

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
# #source("TaylorsLawTools.R")
# 
# #We are only doing spatial taylor's law because we know a priori temporal
# #won't give anything interesting for the surrogates we use
# 
# kend.stats.res<-list()
# kend.points.res<-list()
# spea.stats.res<-list()
# spea.points.res<-list()
# for (counter in 1:length(kend.surrog))
# {
#   ks<-kend.surrog[[counter]]
#   ss<-spea.surrog[[counter]]
#   kend.stats.res[[counter]]<-matrix(NA,5,numdat)
#   spea.stats.res[[counter]]<-matrix(NA,5,numdat)
#   kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
#   spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
#   for (sc in 1:numdat)
#   {
#     khold<-tl_stats(ks[,,sc])
#     kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
#     rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
#     kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)
# 
#     shold<-tl_stats(ss[,,sc])
#     spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
#     rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
#     spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
#   }
# }
# names(kend.stats.res)<-names(kend.surrog)
# names(kend.points.res)<-names(kend.surrog)
# names(spea.stats.res)<-names(spea.surrog)
# names(spea.points.res)<-names(spea.surrog)
```

<!--Now make some plots-->
```{r taylor_plots, echo=T}
##plot TL for clayton
#xlimits<-range(kend.points.res[[1]][,1,],kend.points.res[[2]][,1,],kend.points.res[[3]][,1,],kend.points.res[[4]][,1,])
#ylimits<-range(kend.points.res[[1]][,2,],kend.points.res[[2]][,2,],kend.points.res[[3]][,2,],kend.points.res[[4]][,2,])
#par(mfrow=c(1,1))
#plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
##plot TL for normal copula
#plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for frank
#plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for survival clayton
#plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```
